Making sure the variances converge

### 2024-07-12 Two_var.Rmd
Before a commit night

---
title: "Making sure the variances converge"
output: html_document
date: "2024-07-12"
---

@@

```{r}

```

@@

>>>>

---
title: "Making sure the variances converge"
output:
  pdf_document: default
  html_document: default
date: "2024-07-12"
---

@@

MonteCarlo <- function(n, B, f){
  # n: sample size; B: number of iterations for MC; 
  # f: function to consider (with 2 variables, x and y)
  p <- sum(rep((1/1000)*(1/1000), n))

  # 1st step: generating n samples
  # series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
  col_names <- c()

  series_MC <- data.frame(rep(0,n))
  est_MC <- c()
  for (b in 2:B) {
    x <- paste("x", b, sep = "")
    y <- paste("y", b, sep = "")
    z <- paste("est", b, sep = "")
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    a <- mapply(f, a1, a2)
    est_MC <- append(est_MC, sum(a/p))
    series_MC <- series_MC %>% add_column(x = a1, y = a2, z = a)
    col_names <- append(col_names, c(x, y, z))
  }
  series_MC <- series_MC[,-1]
  colnames(series_MC) <- col_names

  return(c(mean(est_MC), var(est_MC)))
  # Estimated value and Monte-Carlo variance
}
```
rho_MC <- tibble(.rows = n)

```{r}
start.time <- Sys.time()

MC1 <- MonteCarlo(n, 10000, circle_nb)
# Just one circle to begin with

end.time <- Sys.time()
time.taken <- end.time - start.time

time.taken

MC1
```

@@

```{r}
start.time <- Sys.time()

res <- MC_boot(n = 100, B1 = 1000, B2 = 400, f = circle_nb)
# Just one circle to begin with

end.time <- Sys.time()
time.taken <- end.time - start.time

time.taken
```

```{r}
cat("Mean of Monte-Carlo samples:", res[1], "\nMonte-Carlo variance:", res[2], "\nMean of the variance of bootstrap samples:", res[3])
```
